PANCHANGE_analysis

### 2020-09-02 PANCHANGE_analysis.Rmd
Disorder hierarchy chunk amended to match Gerome's request.

```{r dimensions of total dat}
dim(dat.raw)
```

@@

# Vectors for sum_score
```{r Vectors with sum_score_cols}
sum_score_cols <- dat %>%
  select(contains("sum_score")) %>%
  select(-ends_with("raw")) %>%
  colnames()

@@

phq.sum_score_cols <- dat %>%
  select(contains("phq")) %>%
  select(contains("sum_score")) %>% 
  select(-ends_with("raw")) %>%
  select(-contains("8items")) %>%
  colnames()

@@

gad.sum_score_cols <- dat %>%
  select(contains("gad")) %>%
  select(contains("sum_score")) %>% 
  select(-ends_with("raw")) %>%
  colnames()

@@

ocir.sum_score_cols <- dat %>%
  select(contains("ocir")) %>%
  select(contains("sum_score")) %>% 
  select(-ends_with("raw")) %>%
  colnames()

@@

pcl.sum_score_cols <- dat %>%
  select(contains("pcl")) %>%
  select(contains("sum_score")) %>% 
  select(-ends_with("raw")) %>%
  colnames()

@@

# Vectors for diff_score
```{r Vectors with diff_score_cols}
diff_score_cols <- dat %>%
  select(contains("diff_score")) %>% 
  colnames()

@@

phq.diff_score_cols <- dat %>%
  select(contains("phq")) %>%
  select(contains("diff_score")) %>% 
  colnames()

@@

gad.diff_score_cols <- dat %>%
  select(contains("gad")) %>%
  select(contains("diff_score")) %>% 
  colnames()

@@

ocir.diff_score_cols <- dat %>%
  select(contains("ocir")) %>%
  select(contains("diff_score")) %>% 
  colnames()

@@

# Psychiatric disorder hierarchy

control_numeric == 1 ~ 0,
depressive_disorders_numeric == 1 ~ 1,
anxiety_disorders_numeric == 1 ~ 2,
mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 3,
eating_disorders_numeric == 1 ~ 4,
obsessive_compulsive_disorders_numeric == 1 ~ 5,
mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 6,
mhd.personality_disorder_numeric == 1 ~ 7,
autism_spectrum_disorder_numeric == 1 ~ 8,
mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
psychotic_disorders_numeric == 1 ~ 10

psychotic_disorders_numeric == 1 ~ 10
mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
autism_spectrum_disorder_numeric == 1 ~ 8,
mhd.personality_disorder_numeric == 1 ~ 7,
mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 6,
obsessive_compulsive_disorders_numeric == 1 ~ 5,
eating_disorders_numeric == 1 ~ 4,
mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 3,
anxiety_disorders_numeric == 1 ~ 2,
depressive_disorders_numeric == 1 ~ 1,
control_numeric == 1 ~ 0,

```{r Psychiatric disorders hierarchy}
dat <- dat %>%
  mutate(
    Disorder_hierarchical_numeric =
      case_when(
        psychotic_disorders_numeric == 1 ~ 11,
        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 10,
        autism_spectrum_disorder_numeric == 1 ~ 9,
        mhd.personality_disorder_numeric == 1 ~ 8,
        mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 7,
        obsessive_compulsive_disorders_numeric == 1 ~ 6,
        eating_disorders_numeric == 1 ~ 5,
        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
        (anxiety_disorders_numeric == 1 &
        depressive_disorders_numeric == 1) ~ 3,
        anxiety_disorders_numeric == 1 ~ 2,
        depressive_disorders_numeric == 1 ~ 1,
        control_numeric == 1 ~ 0
      )
  )

dat <- dat %>%
  mutate(
    Disorder_hierarchical =
      recode_factor(
        Disorder_hierarchical_numeric,
        `0` = "Controls",
        `1` = "Depressive disorders",
        `2` = "Anxiety disorders",
        `3` = "Depressive & anxiety disorders",
        `4` = "PTSD",
        `5` = "Eating disorders",
        `6` = "OCDs",
        `7` = "ADHD",
        `8` = "Personality disorders",
        `9` = "Autism",
        `10` = "Bipolar disorders",
        `11` = "Psychotic disorders"
      )
  )

dat %>%
  freq(Disorder_hierarchical)
```

Investigate NAs 
Ask Leo?
```{r NAs in diagnosis}
dat %>%
  filter(is.na(Disorder_hierarchical)) %>%
  freq(Sample)
```

>>>>

@@

# Vectors for sum_score

Diagnoses analyses
```{r dat.mhd - Vectors with sum_score_cols}
sum_score_cols <- dat.mhd %>%
  select(contains("sum_score")) %>%
  select(-ends_with("raw")) %>%
  colnames()

@@

phq.sum_score_cols <- dat.mhd %>%
  select(contains("phq")) %>%
  select(contains("sum_score")) %>% 
  select(-ends_with("raw")) %>%
  select(-contains("8items")) %>%
  colnames()

@@

gad.sum_score_cols <- dat.mhd %>%
  select(contains("gad")) %>%
  select(contains("sum_score")) %>% 
  select(-ends_with("raw")) %>%
  colnames()

@@

ocir.sum_score_cols <- dat.mhd %>%
  select(contains("ocir")) %>%
  select(contains("sum_score")) %>% 
  select(-ends_with("raw")) %>%
  colnames()

@@

pcl.sum_score_cols <- dat.mhd %>%
  select(contains("pcl")) %>%
  select(contains("sum_score")) %>% 
  select(-ends_with("raw")) %>%
  colnames()

@@

# Vectors for diff_score

```{r Vectors with diff_score_cols}
diff_score_cols <- dat.mhd %>%
  select(contains("diff_score")) %>% 
  colnames()

@@

phq.diff_score_cols <- dat.mhd %>%
  select(contains("phq")) %>%
  select(contains("diff_score")) %>% 
  colnames()

@@

gad.diff_score_cols <- dat.mhd %>%
  select(contains("gad")) %>%
  select(contains("diff_score")) %>% 
  colnames()

@@

ocir.diff_score_cols <- dat.mhd %>%
  select(contains("ocir")) %>%
  select(contains("diff_score")) %>% 
  colnames()

@@

# Psychiatric disorder hierarchy
------------
OLD VERSIONS:
control_numeric == 1 ~ 0,
depressive_disorders_numeric == 1 ~ 1,
anxiety_disorders_numeric == 1 ~ 2,
mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 3,
eating_disorders_numeric == 1 ~ 4,
obsessive_compulsive_disorders_numeric == 1 ~ 5,
mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 6,
mhd.personality_disorder_numeric == 1 ~ 7,
autism_spectrum_disorder_numeric == 1 ~ 8,
mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
psychotic_disorders_numeric == 1 ~ 10

psychotic_disorders_numeric == 1 ~ 10
mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
autism_spectrum_disorder_numeric == 1 ~ 8,
mhd.personality_disorder_numeric == 1 ~ 7,
mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 6,
obsessive_compulsive_disorders_numeric == 1 ~ 5,
eating_disorders_numeric == 1 ~ 4,
mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 3,
anxiety_disorders_numeric == 1 ~ 2,
depressive_disorders_numeric == 1 ~ 1,
control_numeric == 1 ~ 0,
------------

Disorder hierarchy
1: Psychotic disorders (create one with, create one without to test in analyses)
2: Bipolar disorder
3: MDD
4: PTSD
5: OCD
6: Eating disorders
7: Anxiety disorders

## Hierarchy including psychosis
Diagnoses analyses
```{r Psychiatric disorders hierarchy including psychosis - dat.mhd}
dat.mhd <- dat.mhd %>%
  mutate(
    Disorder_hierarchical_psychosis_numeric =
      case_when(
        psychotic_disorders_numeric == 1 ~ 7,
        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
        depressive_disorders_numeric == 1 ~ 5,
        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
        obsessive_compulsive_disorders_numeric == 1 ~ 3,
        eating_disorders_numeric == 1 ~ 2,
        anxiety_disorders_numeric == 1 ~ 1,
        control_numeric == 1 ~ 0
      )
  )

dat.mhd <- dat.mhd %>%
  mutate(
    Disorder_hierarchical_psychosis =
      recode_factor(
        Disorder_hierarchical_psychosis_numeric,
        `0` = "Controls",
        `1` = "Anxiety disorders",
        `2` = "Eating disorders",
        `3` = "OCDs",
        `4` = "PTSD",
        `5` = "Depressive disorders",
        `6` = "Bipolar disorders",
        `7` = "Psychotic disorders"
      )
  )

dat.mhd %>%
  freq(Disorder_hierarchical_psychosis)
```

Retro-baseline
```{r Psychiatric disorders hierarchy including psychosis - dat.retro}
dat.retro <- dat.retro %>%
  mutate(
    Disorder_hierarchical_psychosis_numeric =
      case_when(
        psychotic_disorders_numeric == 1 ~ 7,
        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
        depressive_disorders_numeric == 1 ~ 5,
        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
        obsessive_compulsive_disorders_numeric == 1 ~ 3,
        eating_disorders_numeric == 1 ~ 2,
        anxiety_disorders_numeric == 1 ~ 1,
        control_numeric == 1 ~ 0
      )
  )

dat.retro <- dat.retro %>%
  mutate(
    Disorder_hierarchical_psychosis =
      recode_factor(
        Disorder_hierarchical_psychosis_numeric,
        `0` = "Controls",
        `1` = "Anxiety disorders",
        `2` = "Eating disorders",
        `3` = "OCDs",
        `4` = "PTSD",
        `5` = "Depressive disorders",
        `6` = "Bipolar disorders",
        `7` = "Psychotic disorders"
      )
  )

dat.retro %>%
  freq(Disorder_hierarchical_psychosis)
```

Prepan-baseline
++MD: For GLAD/EDGI we shouldn't have any controls, but some have crept in because they likely haven't ever received a diagnosis (despite qualifying on the CIDI or current measures of psychopathology). We should consider just excluding them.
```{r Psychiatric disorders hierarchy including psychosis - dat.prepan}
dat.prepan <- dat.prepan %>%
  mutate(
    Disorder_hierarchical_psychosis_numeric =
      case_when(
        psychotic_disorders_numeric == 1 ~ 7,
        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
        depressive_disorders_numeric == 1 ~ 5,
        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
        obsessive_compulsive_disorders_numeric == 1 ~ 3,
        eating_disorders_numeric == 1 ~ 2,
        anxiety_disorders_numeric == 1 ~ 1,
        control_numeric == 1 ~ 0
      )
  )

dat.prepan <- dat.prepan %>%
  mutate(
    Disorder_hierarchical_psychosis =
      recode_factor(
        Disorder_hierarchical_psychosis_numeric,
        `0` = "Controls",
        `1` = "Anxiety disorders",
        `2` = "Eating disorders",
        `3` = "OCDs",
        `4` = "PTSD",
        `5` = "Depressive disorders",
        `6` = "Bipolar disorders",
        `7` = "Psychotic disorders"
      )
  )

dat.prepan %>%
  freq(Disorder_hierarchical_psychosis)
```

## Hierarchy NOT including psychosis
Diagnoses analyses
```{r Psychiatric disorders hierarchy without psychosis - dat.mhd}
dat.mhd <- dat.mhd %>%
  mutate(
    Disorder_hierarchical_numeric =
      case_when(
        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
        depressive_disorders_numeric == 1 ~ 5,
        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
        obsessive_compulsive_disorders_numeric == 1 ~ 3,
        eating_disorders_numeric == 1 ~ 2,
        anxiety_disorders_numeric == 1 ~ 1,
        control_numeric == 1 ~ 0
      )
  )

dat.mhd <- dat.mhd %>%
  mutate(
    Disorder_hierarchical =
      recode_factor(
        Disorder_hierarchical_numeric,
        `0` = "Controls",
        `1` = "Anxiety disorders",
        `2` = "Eating disorders",
        `3` = "OCDs",
        `4` = "PTSD",
        `5` = "Depressive disorders",
        `6` = "Bipolar disorders"
      )
  )

dat.mhd %>%
  freq(Disorder_hierarchical) 
dat.mhd %>% 
  freq(Disorder_hierarchical_psychosis)
```

Retro-baseline
```{r Psychiatric disorders hierarchy without psychosis - dat.retro}
dat.retro <- dat.retro %>%
  mutate(
    Disorder_hierarchical_numeric =
      case_when(
        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
        depressive_disorders_numeric == 1 ~ 5,
        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
        obsessive_compulsive_disorders_numeric == 1 ~ 3,
        eating_disorders_numeric == 1 ~ 2,
        anxiety_disorders_numeric == 1 ~ 1,
        control_numeric == 1 ~ 0
      )
  )

dat.retro <- dat.retro %>%
  mutate(
    Disorder_hierarchical =
      recode_factor(
        Disorder_hierarchical_numeric,
        `0` = "Controls",
        `1` = "Anxiety disorders",
        `2` = "Eating disorders",
        `3` = "OCDs",
        `4` = "PTSD",
        `5` = "Depressive disorders",
        `6` = "Bipolar disorders"
      )
  )

dat.retro %>%
  freq(Disorder_hierarchical)
dat.retro %>%
  freq(Disorder_hierarchical_psychosis)
```

Prepan-baseline
```{r Psychiatric disorders hierarchy without psychosis - dat.prepan}
dat.prepan <- dat.prepan %>%
  mutate(
    Disorder_hierarchical_numeric =
      case_when(
        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
        depressive_disorders_numeric == 1 ~ 5,
        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
        obsessive_compulsive_disorders_numeric == 1 ~ 3,
        eating_disorders_numeric == 1 ~ 2,
        anxiety_disorders_numeric == 1 ~ 1,
        control_numeric == 1 ~ 0
      )
  )

dat.prepan <- dat.prepan %>%
  mutate(
    Disorder_hierarchical =
      recode_factor(
        Disorder_hierarchical_numeric,
        `0` = "Controls",
        `1` = "Anxiety disorders",
        `2` = "Eating disorders",
        `3` = "OCDs",
        `4` = "PTSD",
        `5` = "Depressive disorders",
        `6` = "Bipolar disorders"
      )
  )

dat.prepan %>%
  freq(Disorder_hierarchical)
dat.prepan %>%
  freq(Disorder_hierarchical_psychosis)
```

Investigate NAs 
Ask Leo?
++MD: you'll have NAs for individuals that don't have one of the listed disorders in the hierarchy, but who have another diagnosis that excludes them from being a control (e.g. personality disorder, ADHD, ASD). We can add an "Other" category to cover those other diagnoses, or exclude them from these analyses.
```{r NAs in diagnosis}
dat.mhd %>%
  filter(is.na(Disorder_hierarchical)) %>%
  freq(Sample)

dat.retro %>%
  filter(is.na(Disorder_hierarchical)) %>%
  freq(Sample)

dat.prepan %>%
  filter(is.na(Disorder_hierarchical)) %>%
  freq(Sample)
```
